### 2021-05-14 docs/manuscript/PLOS-MSc-Thesis.tex
Add description of figure S3

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Most GRNs reach the steady state before 250 time steps.}
GRN number 660 displaying the topology number 33 (A) and its spatiotemporal
expression profile (B).

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Bridge topologies in the neutral network.}

>>>>

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Most GRNs reach the steady state before 250 time steps.}
(A) Gene regulatory network displaying the topology number 33. (B) Spatiotemporal
expression profile of the gene regulatory network shown in (A).

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Bridge topologies in the neutral network.}
``Bridge topologies'' are those topologies that connect two clusters in the neutral
network (Fig~\ref{fig:neutral-network}), and as such can be interpreted as
intermediary steps in the evolution from a cluster of related topologies into
another cluster. For example the topology 441 could be an initial step to reach the
topology 9, as in this topology nodes B and C are not connected.
